The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
revert title
example -> case study

---
title: Considering scale in multilayer animal social networks
author:
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
    correspondence: true
  - name: Quinn M.R. Webber
    institute: cabe
  - name: Julie W. Turner
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, scale-dependent social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. Furthermore,
sociality can vary within and across seasons. Multilayer networks promise the 
explicit integration of
the social, spatial and, temporal contexts. Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains an
important gap in our understanding of the influence of scale on animal social
networks. Using an empirical example, we discuss ways of considering social, spatial and, temporal scale in
the context of multilayer caribou social networks. Effective
integration of social and spatial processes, including biologically meaningful
scales, within the context of animal social networks is an emerging area of
research. We incorporate perspectives that link the social environment to spatial
processes across scales in a multilayer context.

>>>>

---
title: The problem and promise of scale in animal social multilayer networks
author:
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
    correspondence: true
  - name: Quinn M.R. Webber
    institute: cabe
  - name: Julie W. Turner
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, scale-dependent social processes can range from
fine-scale interactions to co-occurrence and overlapping home ranges.
Furthermore, sociality can vary within and across seasons. Multilayer networks
promise the explicit integration of the social, spatial and, temporal contexts.
Given the complex interplay of sociality and animal space use in heterogeneous
landscapes, there remains an important gap in our understanding of the influence
of scale on animal social networks. Using an empirical case study, we discuss
ways of considering social, spatial and, temporal scale in the context of
multilayer caribou social networks. Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research. We incorporate
perspectives that link the social environment to spatial processes across scales
in a multilayer context.
